Imputation of incomplete multilevel data

### 2024-02-29 manuscript.qmd
update mechanisms
add callout

::: {callout-info}
# why
this

:::

The second scenario is that the available information is not sufficient to arrive at the correct conclusion. In this case, we need to apply some modeling to arrive at the correct conclusion. Rubin (1987) defines this scenario as **missing at random** (MAR). The third scenario is that the available information is not sufficient to arrive at the correct conclusion, but that the available information allows us to model the missing information in such a way that we can arrive at the correct conclusion. Rubin (1987) defines this scenario as **missing not at random** (MNAR).
This is the ideal scenario, but it is not always the case. The second scenario is that the available information is not sufficient to arrive at the correct conclusion. In this case, we need to apply some modeling to arrive at the correct conclusion. The third scenario is that the available information is not sufficient to arrive at the correct conclusion, but that the available information allows us to model the missing information in such a way that we can arrive at the correct conclusion. This is the scenario that we will focus on in this tutorial.

You may have recognized that we speak very carefully of information.

Incomplete data are ubiquitous in science. People often make the assumption that incomplete data are the result of human subject research, where participants may not reposnd to all questions or may drop out of a study.  Incomplete data are often the result of human subjects research, where participants may not respond to all questions or may drop out of the study. Incomplete data may also occur in other types of research, such as in the social sciences, where data may be missing due to administrative errors or other reasons. Incomplete data may be resolved, but need to be handled in accordance with the analysis of scientific interest. In human-subjects research, there is often clustering, which may be captured with multilevel modeling techniques. If the analysis of scientific interest is a multilevel model, the missing data handling method should accommodate the multilevel structure of the data. Both missingness and multilevel structures require advanced statistical techniques. This tutorial sets out to facilitate empirical researchers in accommodating both multilevel structures as well as missing data. We illustrate the use of the software by means of a case study.
1. missing data occur often in data with human subjects
2. missing data may be resolved, but need to be handled in accordance with the analysis of scientific interest
3. in human-subjects research, there is often clustering, which may be captured with multilevel modeling techniques
4. if the analysis of scientific interest is a multilevel model, the missing data handling method should accommodate the multilevel structure of the data
4. both missingness and multilevel structures require advanced statistical techniques
5. this tutorial sets out to facilitate empirical researchers in accommodating both multilevel structures as well as missing data
6. we illustrate the use of the software by means of a case study

>>>>

::: {.callout-info}
# why not distinguish between missingness mechanisms
explanation needed
:::

1. missing data occur often in data with human subjects
2. missing data may be resolved, but need to be handled in accordance with the analysis of scientific interest
3. in human-subjects research, there is often clustering, which may be captured with multilevel modeling techniques
4. if the analysis of scientific interest is a multilevel model, the missing data handling method should accommodate the multilevel structure of the data
4. both missingness and multilevel structures require advanced statistical techniques
5. this tutorial sets out to facilitate empirical researchers in accommodating both multilevel structures as well as missing data
6. we illustrate the use of the software by means of a case study
